Evidence for a Color Parameter Unassociated With Dust Within the Type~Ia Supernovae of the Nearby Supernova Factory

### 2017-03-26 apj.tex
simulated model 11

\begin{abstract}
An empirical model for SN~Ia peak magnitudes with two color parameters and dependence on the equivalent widths of CaII, SiII, and SiII velocity
is applied to the supernova sample of the Nearby Supernova Factory.  The peak magnitudes in synthetic
broadband photometry and their colors are found to be 
dependent on the spectral equivalent widths and the color parameters, to better than 
%-----
$(1-5\times10^{-5})$
%------
confidence.
The color changes allowed by the model are almost parallel to the color changes allowed by the dust model of  \citet{1999PASP..111...63F} with floating
total-to-selective extinction parameter $R^F$.  The prior of no parameter covariance used in the training, and the deduced extinctions and color excess
are both qualitatively consistent with $R^F \sim 2.4$.
The derived dust curve is able to reproduce the optical colors of the highly reddened SN~2014J better than the \citet{1999PASP..111...63F} dust model.
Inspired that our  two-parameter model, with no conditioning that would steer it toward a dust model, produces behavior similar to that expected from Galactic dust, we extend  the model to three color parameters.
In this new case we obtain consistent results for
all the parameters in common,
plus a detection of a third parameter at
%--- table.py
$(1-5\times10^{-4})$
%-----
confidence;
this new parameter represents supernova color diversity
beyond that tracked by the spectral features and two-parameter dust models.
A direct incorporation of dust models into our formalism is impossible. An indirect incorporation of dust
yields in constant-$R^F$ model $R^F \sim 3$, but the implementation is sensitive to systematic uncertainties that arise
from the need to specify the colors of an unextincted supernova and its use of absolute extinction, neither of which is used in our original model.
\end{abstract}

@@

We now compare our model and its color-coefficient parameters $\gamma^0$ and $\gamma^1$ with the expectations of  dust models.
A direct analysis of the  \citetalias{1999PASP..111...63F} dust model is presented later
in \S\ref{model0:sec}.

@@

The 2-parameter linear model
\begin{equation}
A_X = a(X)  A_V + b(X) E(B-V)
\label{f99:eqn}
\end{equation}
approximately describes dust models.
For the case of
$R^F=2.5$ and $A^F_V=0.1$,
and the measurement of the SALT2
\citet{2007A&A...466...11G} $s=1$, $x_1=0$ SN~Ia template at $B$-band peak, the \citetalias{1999PASP..111...63F} model
gives
$a(U,B,V,R,I)=\{0.96,   1.00,   1.00,   0.97,   0.77\}$ and $b(U,B,V,R,I)=\{  1.77,   0.98,   0.12,  -0.50,  -0.53\}$.
The $F$ superscript is added to distinguish \citetalias{1999PASP..111...63F} parameters.
Over the ranges of
 $R^F$ and $A^F_V$,
and the wavelengths under consideration,  the values of the elements of $a$ and $b$ change but only by $<5$\%.

@@

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.95in]{output11/plane0.pdf}
   \includegraphics[width=2.95in]{output11/plane1.pdf}
   \includegraphics[width=2.95in]{output11/plane0BVR.pdf}
   \includegraphics[width=2.95in]{output11/plane1BVR.pdf}
   \caption{
   Two perspectives (left and right columns) of $UVI$- (top row) and $BVR$- (bottom row) spaces
of the vectors corresponding to $\gamma^i_X/(\gamma^i_B-\gamma^i_V)$ of our model (solid lines),
   and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  The combinations $a(X)+b(X)/2.4$ and  $a(X)+b(X)/2.6$ are shown in the dotted
   lines: thy are almost perfectly superimposed on $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$ for $UVI$ and $BVR$ respectively.  $b(X)$ shown in the dotted line is
   almost  perfectly superimposed on $\gamma^1_X/(\gamma^1_B-\gamma^1_V)$ in $UVI$ but is clearly distinct in $BVR$.  
   \label{plane:fig}}
\end{figure}

@@

Now consider what happens when supernovae can have small  perturbations away from that constant $R^F$ value.  Each supernova magnitude
can be described as the sum of the contribution along the $a(X)+b(X)/R^F$ direction, plus a perturbation in a different direction due its deviation  from $R_V$.
The zero-correlation condition, which determines the direction of $\gamma^1$,  is for the coordinate values along $\gamma^0$ to be uncorrelated with the coordinate values along $\gamma^1$.
Our analysis yields an angle of 154\arcdeg between  $\gamma^0$ and $\gamma^1$.
The vectors not being perpendicular arises because the distribution of the perturbations in $R^F$ are dependent on the amount of first-order $R_V$ extinction.
Perturbations away from $R^F$ and their correlation with extinction also shift the direction of $\gamma^0$.

@@

\color{black}
The analysis is validated using simulated datasets with and without third color parameters: the input parameters are recovered within  uncertainties.
\color{blue}
We present here the results of one of the validation tests.  The input values of the supernova parameters are the median values from the analysis of real data.
Ten realizations of simulated data are generated based on the data covariances, and then analyzed separately.   The posteriors of the ten realizations
are aggregated and shown in Figures~\ref{simglobal1:fig}--\ref{simglobal5:fig}.  The input parameters are recovered well
within the 68\% credible interval.  There is a tendency for the slope parameters to be slightly underestimated, which is an expected consequence of 
the uncertainties in the predictor variable, which in turn lead to 
regression dilution.  Our analysis is susceptible to this bias because we do consciously do not include distributions
of supernova parameters as part of our model.

@@

\color{black}
\section{Supernova Model III: Fitzpatrick Dust}
\label{model0:sec}
\color{blue}
Dust models can explain the extrinsic magnitude and color variations found in
the linear models of \S\ref{model:sec} and \S\ref{model2:sec}.  In this section, we 
perform a more conventional analysis by replacing the $\gamma k$ color terms with extinction
terms predicted by a dust extinction model from the literature.  
%
%We analyze our data with a model that incorporates attenuation due to host-galaxy dust: it is identical to that of \S\ref{model:sec}
%except that dust
%is used in place of  the linear two-color-parameter  model.      
The dust model of  \citet{1999PASP..111...63F} is considered:
while commonly used dust
models are qualitatively similar in the optical wavelengths relevant to our data, that of  \citetalias{1999PASP..111...63F} 
does relatively well in reproducing supernova observations \citep{2041-8205-788-2-L21, 2016AAS...22723705H}.

The  \citetalias{1999PASP..111...63F} dust model has two parameters, $R^F$ and $E^F(B-V)$.  The first, $R^F$,
specifies the wavelength-dependent  attenuation  that we notate as $A^F/E^F(B-V)$.  The second, $E^F(B-V)$, specifies the normalization
of that attenuation.  These two parameters can be combined to define a third dependent parameter $A^F_V \equiv R^F E^F(B-V)$.
The dust model is expressed as
\begin{equation}
A(\lambda; E^F(B-V), R^F) = E^F(B-V) \frac{A^F}{E^F(B-V)}\left(\lambda; R^F \right).
\end{equation}

In the broadband photometry of a source with SED $f(\lambda)$ observed in a filter with transmission $X$, the attenuation $A_X$ is
\begin{equation}
A_X\left(A^F_V, E^F(B-V)  \right) = 2.5 \log{\left(\frac{\int f(\lambda) X(\lambda)d\lambda}{\int 10^{-0.4 A\left(\lambda; E^F(B-V), R^F=\frac{A^F_V}{E^F(B-V)}\right)} f(\lambda) X(\lambda)d\lambda } \right)},
\end{equation}
whose first-order approximation
\begin{equation}
A_X\left(A^F_V, E^F(B-V)  \right) = \frac{\int  A\left(\lambda; E^F(B-V), R^F=\frac{A^F_V}{E^F(B-V)}\right)f(\lambda) X(\lambda)d\lambda}{\int  f(\lambda) X(\lambda)d\lambda}
\end{equation}
is easy to interpret as an effective extinction.

We are  faced with a conundrum: our broad-band model does not specify $f(\lambda)$.  As an ansatz,
the SED of the SALT2 (v2.4), $c=0$, $x_1=0$ supernova at peak $B$ brightness is adopted as the SED of an unextincted
SN~Ia, independent of spectral-feature parameters.  This choice contrasts with the models in the previous sections, which do not specify the
parameter values of an unextincted
supernova.
The SALT2 SED determines the values of $A_X$ and the
intrinsic colors.

This ansatz is  inconsistent with the results of the linear models evaluated with SNf data presented in previous sections in that the colors of a canonical supernova are not accessible by a SALT2 SED experiencing  \citetalias{1999PASP..111...63F} dust.
Taking the SALT2 template as the unextincted supernova, the canonical supernova with colors given by the best-fit $c_X$'s in \S\ref{model:sec} has the broad-band color excesses $E(X-V)$ shown in
Figure~\ref{model1118:fig}.  Overplotted are representative $E(X-V)$  allowed by dust.
The canonical supernova is in tension with colors induced by dust at extreme wavelengths, toward the red in the $U$ but blue in the $I$,
while simultaneously showing no color excess is $B-R$.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output18/model1118ebv.pdf}
   \includegraphics[width=2.8in]{output18/comptolinear.pdf}
    \caption{Left: Broad-band color excesses $E(X-V)$ of the best-fit $c$'s of \S\ref{model:sec} 
    taking the SALT2 template as an unextinced supernova.  Overplotted are possible $E(X-V)$ for a fixed $A_V$ and a range of $R$,
allowed by \citetalias{1999PASP..111...63F} dust.
Right:    $A_X/E(X-V)$ of the best-fit $c$'s 
    relative to SALT2. \label{model1118:fig}}
\end{figure}

%
%We emphasize now that our broadband magnitude model does not ambiguously specify $A_X$, which depend
%on the SED of the source.  
%In our model for broadband magnitudes, the SEDs of supernovae $f(\lambda)$ are not specified.  In its place we use the 
%updated \citet{2007ApJ...663.1187H} template at peak (the $x_1=0$, $c=0$
%SALT2 template yields similar results.)
%The Hsiao template does not perfectly represent the underlying spectrum of a supernova and hence is a source
%of model error.  Consider the SED to be the sum of the template and an offset
%\begin{equation}
%f(\lambda) = f_{Hsiao}(\lambda) + \delta f(\lambda).
%\end{equation}
%To first order, deviations of the true spectrum from the template yield small additive and multiplicative corrections to the template-based
%extinction.  Heterogeneity in the true spectrum amongst supernovae produce scatter on top of those corrections.

%For the purposes of efficiency in our fitter algorithm, we approximate the \citetalias{1999PASP..111...63F} dust model in the range
%$-0.21 \le A_V \le 1.8$, $2.1 \le R \le 6.9$ with a third-order polynomial in $A_V$ and $E(B-V)$.   The limits in $R$ represent the range of
%values that enter the dust-model training.
%The differences between the extinction and the polynomial approximation are small relative to  $\partial A_X/ \partial R$ over the scales of
%$R$ of interest.

%
%
%
%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%   \centering
%   \includegraphics[width=5.2in]{output18/dfitz.pdf}
%    \caption{Residuals between the  broadband extinction of the updated \citet{2007ApJ...663.1187H} template at peak due to $A_V=1.8$
%    \citetalias{1999PASP..111...63F} dust,  and the polynomial approximation used in this analysis.
%   \label{dfitz:fig}}
%\end{figure}
%

The model we consider in this section is identical to the linear model described by Eqns.~\ref{ewsiv:eqn}
and
\ref{dust:eqn} in \S\ref{model:sec}, except that the colors of a zero-extinction supernova (parameterized by differences in $c_X$) are fixed to those of the SALT2 template,
and the $\gamma k$ terms are replaced with $A_X(A_V=R E(B-V), E(B-V))$.   Each supernova has an $E(B-V)$ parameter 
and there is one global $R$ parameter.  
%
%
%Three distinct analyses are run with the  \citetalias{1999PASP..111...63F}  dust model.  In the first (denoted
%as $R=const$), $R$ is held the same for all supernovae.  In the second  (denoted as $\ln{R} \sim \mathcal{N}$),
%the $\ln{R}$ for each supernova is taken to be drawn from a Normal distribution with dispersion $\sigma_{\ln{R}}$.
%In the third (denoted as $R$-free), $A_V$ and $R$ are free for
%each supernova, with a uniform prior $-0.21\le A_V \le 1.8$, $2.1 \le R \le 6.9$.

Results from evaluating this model with SNf data
provide further evidence of the inconsistency between the ansatz and the models of the previous section.
The dust-model analysis of this section sets the magnitude of an $A_V=0$ supernova, so now  magnitudes of the canonical
supernova in \S\ref{model:sec} can also be compared (along with color) to the expectations of the dust model.  The magnitude difference, $\Delta c_X$,
is the difference between the $c_X$ parameters of the two analyses.
Then  $\Delta c_X / (\Delta c_B - \Delta c_V)$
corresponds to  $A_X/E(B-V)$ of the canonical supernova relative
to SALT2: these values are plotted in
Figure~\ref{model1118:fig}.
The negative values for $X=BVRI$ and the non-monotonic behavior is inconsistent with the expectations of dust.

The analysis results for the dust parameters are shown in Figure~\ref{AVRV:fig}.  The left plot shows the histogram of the median $A_V$ determined for
each supernova. The
$A_V$ distribution  has a slow rise from zero; recall that the equivalent $\gamma^0_V k_0$
from the linear model of \S\ref{model:sec} has the sharp rise expected from of a large fraction of supernovae
experiencing no dust \citep{1998ApJ...502..177H}. The right plot shows the posterior of $R$, with 68\% credible interval
$R=2.99^{0.18}_{-0.16}$.  We perform the same analysis using the updated template of \citet{2007ApJ...663.1187H} in place of SALT2.
While the $A_V$ distributions using the different models appear similar, there is a significant shift in the $R$ distribution
to $R=3.17^{0.20}_{-0.17}$.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output18/AVs_mode_hist.pdf}
   \includegraphics[width=2.8in]{output18/RVs_hist.pdf}
    \caption{Left: Histogram of the median $A_V$ determined for
each supernova.  The $\gamma^0_V k_0$ medians from our 2-parameter model of \S\ref{model:sec} is also shown.  The means of the measurement
uncertainty over all supernovae are 0.13,   0.16,   0.11, and  0.05 mag respectively, roughly the size of the bin.
Right: Posteriors for $R$.  Results for both the SALT2 supernova model and the updated \citet{2007ApJ...663.1187H} are shown.
   \label{AVRV:fig}}
\end{figure}

The broadband nature of our supernova model does not allow a precise specification for the prediction of dust models,
and our ansatz for incorporating dust is limited systematically in measuring 
the total-to-selective extinction.  We emphasize also that $R^F$ determined in this section are based on  both absolute extinction and color,
whereas the $\gamma$'s (and resulting $\kappa_1$) in \S\ref{model:sec} do not depend on absolute extinction, i.e. the extra model constraint  of the
zero-extinction supernova.

%
%The $R$-free analysis is performed for the dust law of \citet{1989ApJ...345..245C}.  Figure~\ref{CCMF99:fig} shows the difference between per-supernova
%$A_V$ and $R_V$ of  the  \citet{1989ApJ...345..245C} (superscripted with $C$) and \citetalias{1999PASP..111...63F} dust laws.
%The weighted mean of the difference in $A_V$ is $0.06 \pm 0.01$ mag and that of $R_V$ is $-0.26 \pm 0.09$, both significantly
%non-zero.  Insofar that the $A_V$ and $R_V$
%parameters of the two models are designed to represent the same dust observables, we find that the systematic uncertainty in the dust model itself
%is important.
%
%
%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%   \centering
%   \includegraphics[width=5.2in]{output18/CCMf99.pdf}
%    \caption{Difference between per-supernova
%$A_V$ and $R_V$ of the  \citet{1989ApJ...345..245C} and \citetalias{1999PASP..111...63F} dust laws.
%   \label{CCMF99:fig}}
%\end{figure}

\color{black}
\section{Discussion and Summary}
\label{discussion:sec}

@@

\color{blue}
An interesting direction for future work is to use narrower bands for generating synthetic photometry.  When the bandwidth were small enough
to resolve spectral features, the analysis would produce a spectroscopic model.   Higher resolution would allow us to forego 
the use of a fiducial template necessary to predict broadband fluxes generated by dust models.
\color{black}

>>>>

\begin{abstract}
An empirical model for SN~Ia peak magnitudes with two color parameters and dependence on the equivalent widths of CaII, SiII, and SiII velocity
is applied to the supernova sample of the Nearby Supernova Factory.  The peak magnitudes in synthetic
broadband photometry and their colors are found to be 
dependent on the spectral equivalent widths and the color parameters, to better than 
%-----
$(1-5\times10^{-5})$
%------
confidence.
The color changes allowed by the model are almost parallel to the color changes allowed by the dust model of  \citet{1999PASP..111...63F} with floating
total-to-selective extinction parameter $R^F$.  The prior of no parameter covariance used in the training, and the deduced extinctions and color excess
are both qualitatively consistent with $R^F \sim 2.4$.
The derived dust curve is able to reproduce the optical colors of the highly reddened SN~2014J better than the \citet{1999PASP..111...63F} dust model.
Inspired that our  two-parameter model, with no conditioning that would steer it toward a dust model, produces behavior similar to that expected from Galactic dust, we extend  the model to three color parameters.
In this new case we obtain consistent results for
all the parameters in common,
plus a detection of a third parameter at
%--- table.py
$(1-5\times10^{-4})$
%-----
confidence;
this new parameter represents supernova color diversity
beyond that tracked by the spectral features and two-parameter dust models.
%A direct incorporation of dust models into our formalism is impossible. An indirect incorporation of dust
%yields in constant-$R^F$ model $R^F \sim 3$, but the implementation is sensitive to systematic uncertainties that arise
%from the need to specify the colors of an unextincted supernova and its use of absolute extinction, neither of which is used in our original model.
\end{abstract}

@@

@@

We now compare our model and its color-coefficient parameters $\gamma^0$ and $\gamma^1$ with the expectations of  dust models.
The 2-parameter linear model
\begin{equation}
A_X = a(X)  A_V + b(X) E(B-V)
\label{f99:eqn}
\end{equation}
approximately describes dust models.
For the case of
$R^F=2.5$ and $A^F_V=0.1$,
and the measurement of the SALT2
\citet{2007A&A...466...11G} $s=1$, $x_1=0$ SN~Ia template at $B$-band peak, the \citetalias{1999PASP..111...63F} model
gives
$a(U,B,V,R,I)=\{0.96,   1.00,   1.00,   0.97,   0.77\}$ and $b(U,B,V,R,I)=\{  1.77,   0.98,   0.12,  -0.50,  -0.53\}$.
The $F$ superscript is added to distinguish \citetalias{1999PASP..111...63F} parameters.
Over the ranges of
 $R^F$ and $A^F_V$,
and the wavelengths under consideration,  the values of the elements of $a$ and $b$ change but only by $<5$\%.

@@

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.95in]{output11/plane0.pdf}
   \includegraphics[width=2.95in]{output11/plane1.pdf}
   \includegraphics[width=2.95in]{output11/plane0BVR.pdf}
   \includegraphics[width=2.95in]{output11/plane1BVR.pdf}
   \caption{
   Two perspectives (left and right columns) of $UVI$- (top row) and $BVR$- (bottom row) spaces
of the vectors corresponding to $\gamma^i_X/(\gamma^i_B-\gamma^i_V)$ of our model (solid lines),
   and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines).  The combinations $a(X)+b(X)/2.4$ and  $a(X)+b(X)/2.6$ are shown in the dotted
   lines: they are almost perfectly superimposed on $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$ for $UVI$ and $BVR$ respectively.  $b(X)$ shown in the dotted line is
   almost  perfectly superimposed on $\gamma^1_X/(\gamma^1_B-\gamma^1_V)$ in $UVI$ but is clearly distinct in $BVR$.  
   \label{plane:fig}}
\end{figure}

@@

Now consider what happens when supernovae can have small  perturbations away from that constant $R^F$ value.  Each supernova magnitude
can be described as the sum of the contribution along the $a(X)+b(X)/R^F$ direction, plus a perturbation in a different direction due its deviation  from $R_V$.
The zero-correlation condition, which determines the direction of $\gamma^1$,  is for the coordinate values along $\gamma^0$ to be uncorrelated with the coordinate values along $\gamma^1$.
Our analysis yields an angle of 154\arcdeg\ between  $\gamma^0$ and $\gamma^1$.
The vectors not being perpendicular arises because the distribution of the perturbations in $R^F$ are dependent on the amount of first-order $R_V$ extinction.
Perturbations away from $R^F$ and their correlation with extinction also shift the direction of $\gamma^0$.

As a check of the above interpretation, we generate a simulated dataset with the same numbers and uncertainties as our data, based on a
SALT2 $x_1=0$, $c=0$ template and  \citetalias{1999PASP..111...63F} dust.  The supernovae
are assigned $E^F(B-V)$ parameters equal to the $B-V$ color excesses determined in our sample, and $R^F$ values drawn from a log-normal
distribution with a mean of $2.4$ and 0.05 standard deviation.  The $\alpha$, $\beta$, and $\eta$ parameters are set to zero, so that dust and
measurement uncertainty are the only sources of variation in magnitudes.  As with the analysis of our data, we find that the
$\gamma$'s and \citetalias{1999PASP..111...63F}  vectors for nearly parallel planes, with the $\gamma^0$ vector consistent with
$\kappa_1=1/2.3$.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.95in]{output11_sim/plane0.pdf}
   \includegraphics[width=2.95in]{output11_sim/plane1.pdf}
   \caption{
   Two perspectives of $UVI$- spaces
of the vectors corresponding to $\gamma^i_X/(\gamma^i_B-\gamma^i_V)$ of our model (solid lines),
   and $a(X)$, $b(X)$ of the \citetalias{1999PASP..111...63F} model (dashed lines), for a simulated dataset with
   input $R^F$ drawn from a log-normal distribution  with a mean of $2.4$ and 0.05 standard deviation.
   The combinations $a(X)+b(X)/2.3$ and  $a(X)+b(X)/2.4$ are shown in the dotted
   lines, the former is 
   almost  perfectly  superimposed on  $\gamma^0_X/(\gamma^0_B-\gamma^0_V)$.
   \label{plane_sim:fig}}
\end{figure}

@@

\color{black}
The analysis is validated using simulated datasets with and without third color parameters: the input parameters are recovered within  uncertainties.
\color{blue}
We present here the results of one of the validation tests.  The input values of the supernova parameters are the median values from the analysis of real data.
Ten realizations of simulated data are generated based on the data covariances, and then analyzed separately.   The posteriors of the ten realizations
are aggregated and shown in Figures~\ref{simglobal1:fig}--\ref{simglobal5:fig}.  The input parameters are recovered with negligible bias
relative to the statistical uncertainties.  There is a tendency for the slope parameters to be slightly underestimated, which is an expected consequence of 
the uncertainties in the predictor variable, which in turn lead to 
regression dilution.  Our analysis is susceptible to this bias because we do consciously do not include distributions
of supernova parameters as part of our model.

@@

\color{black}
%\section{Supernova Model III: Fitzpatrick Dust}
%\label{model0:sec}
%\color{blue}
%Dust models can explain the extrinsic magnitude and color variations found in
%the linear models of \S\ref{model:sec} and \S\ref{model2:sec}.  In this section, we 
%perform a more conventional analysis by replacing the $\gamma k$ color terms with extinction
%terms predicted by a dust extinction model from the literature.  
%%
%%We analyze our data with a model that incorporates attenuation due to host-galaxy dust: it is identical to that of \S\ref{model:sec}
%%except that dust
%%is used in place of  the linear two-color-parameter  model.      
%The dust model of  \citet{1999PASP..111...63F} is considered:
%while commonly used dust
%models are qualitatively similar in the optical wavelengths relevant to our data, that of  \citetalias{1999PASP..111...63F} 
%does relatively well in reproducing supernova observations \citep{2041-8205-788-2-L21, 2016AAS...22723705H}.
%
%
%The  \citetalias{1999PASP..111...63F} dust model has two parameters, $R^F$ and $E^F(B-V)$.  The first, $R^F$,
%specifies the wavelength-dependent  attenuation  that we notate as $A^F/E^F(B-V)$.  The second, $E^F(B-V)$, specifies the normalization
%of that attenuation.  These two parameters can be combined to define a third dependent parameter $A^F_V \equiv R^F E^F(B-V)$.
%The dust model is expressed as
%\begin{equation}
%A(\lambda; E^F(B-V), R^F) = E^F(B-V) \frac{A^F}{E^F(B-V)}\left(\lambda; R^F \right).
%\end{equation}
%
%In the broadband photometry of a source with SED $f(\lambda)$ observed in a filter with transmission $X$, the attenuation $A_X$ is
%\begin{equation}
%A_X\left(A^F_V, E^F(B-V)  \right) = 2.5 \log{\left(\frac{\int f(\lambda) X(\lambda)d\lambda}{\int 10^{-0.4 A\left(\lambda; E^F(B-V), R^F=\frac{A^F_V}{E^F(B-V)}\right)} f(\lambda) X(\lambda)d\lambda } \right)},
%\end{equation}
%whose first-order approximation
%\begin{equation}
%A_X\left(A^F_V, E^F(B-V)  \right) = \frac{\int  A\left(\lambda; E^F(B-V), R^F=\frac{A^F_V}{E^F(B-V)}\right)f(\lambda) X(\lambda)d\lambda}{\int  f(\lambda) X(\lambda)d\lambda}
%\end{equation}
%is easy to interpret as an effective extinction.
%
%
%We are  faced with a conundrum: our broad-band model does not specify $f(\lambda)$.  As an ansatz,
%the SED of the SALT2 (v2.4), $c=0$, $x_1=0$ supernova at peak $B$ brightness is adopted as the SED of an unextincted
%SN~Ia, independent of spectral-feature parameters.  This choice contrasts with the models in the previous sections, which do not specify the
%parameter values of an unextincted
%supernova.
%The SALT2 SED determines the values of $A_X$ and the
%intrinsic colors. 
%
%This ansatz is  inconsistent with the results of the linear models evaluated with SNf data presented in previous sections in that the colors of a canonical supernova are not accessible by a SALT2 SED experiencing  \citetalias{1999PASP..111...63F} dust.
%Taking the SALT2 template as the unextincted supernova, the canonical supernova with colors given by the best-fit $c_X$'s in \S\ref{model:sec} has the broad-band color excesses $E(X-V)$ shown in
%Figure~\ref{model1118:fig}.  Overplotted are representative $E(X-V)$  allowed by dust.
%The canonical supernova is in tension with colors induced by dust at extreme wavelengths, toward the red in the $U$ but blue in the $I$,
%while simultaneously showing no color excess is $B-R$.
% 
%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%   \centering
%   \includegraphics[width=2.8in]{output18/model1118ebv.pdf}
%   \includegraphics[width=2.8in]{output18/comptolinear.pdf}
%    \caption{Left: Broad-band color excesses $E(X-V)$ of the best-fit $c$'s of \S\ref{model:sec} 
%    taking the SALT2 template as an unextinced supernova.  Overplotted are possible $E(X-V)$ for a fixed $A_V$ and a range of $R$,
%allowed by \citetalias{1999PASP..111...63F} dust.
%Right:    $A_X/E(X-V)$ of the best-fit $c$'s 
%    relative to SALT2. \label{model1118:fig}}
%\end{figure}
%
%
%%
%%We emphasize now that our broadband magnitude model does not ambiguously specify $A_X$, which depend
%%on the SED of the source.  
%%In our model for broadband magnitudes, the SEDs of supernovae $f(\lambda)$ are not specified.  In its place we use the 
%%updated \citet{2007ApJ...663.1187H} template at peak (the $x_1=0$, $c=0$
%%SALT2 template yields similar results.)
%%The Hsiao template does not perfectly represent the underlying spectrum of a supernova and hence is a source
%%of model error.  Consider the SED to be the sum of the template and an offset
%%\begin{equation}
%%f(\lambda) = f_{Hsiao}(\lambda) + \delta f(\lambda).
%%\end{equation}
%%To first order, deviations of the true spectrum from the template yield small additive and multiplicative corrections to the template-based
%%extinction.  Heterogeneity in the true spectrum amongst supernovae produce scatter on top of those corrections.
%
%%For the purposes of efficiency in our fitter algorithm, we approximate the \citetalias{1999PASP..111...63F} dust model in the range
%%$-0.21 \le A_V \le 1.8$, $2.1 \le R \le 6.9$ with a third-order polynomial in $A_V$ and $E(B-V)$.   The limits in $R$ represent the range of
%%values that enter the dust-model training.
%%The differences between the extinction and the polynomial approximation are small relative to  $\partial A_X/ \partial R$ over the scales of
%%$R$ of interest.
%
%%
%%
%%
%%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%%   \centering
%%   \includegraphics[width=5.2in]{output18/dfitz.pdf}
%%    \caption{Residuals between the  broadband extinction of the updated \citet{2007ApJ...663.1187H} template at peak due to $A_V=1.8$
%%    \citetalias{1999PASP..111...63F} dust,  and the polynomial approximation used in this analysis.
%%   \label{dfitz:fig}}
%%\end{figure}
%%
%
%
%The model we consider in this section is identical to the linear model described by Eqns.~\ref{ewsiv:eqn}
%and
%\ref{dust:eqn} in \S\ref{model:sec}, except that the colors of a zero-extinction supernova (parameterized by differences in $c_X$) are fixed to those of the SALT2 template,
%and the $\gamma k$ terms are replaced with $A_X(A_V=R E(B-V), E(B-V))$.   Each supernova has an $E(B-V)$ parameter 
%and there is one global $R$ parameter.  
%%
%%
%%Three distinct analyses are run with the  \citetalias{1999PASP..111...63F}  dust model.  In the first (denoted
%%as $R=const$), $R$ is held the same for all supernovae.  In the second  (denoted as $\ln{R} \sim \mathcal{N}$),
%%the $\ln{R}$ for each supernova is taken to be drawn from a Normal distribution with dispersion $\sigma_{\ln{R}}$.
%%In the third (denoted as $R$-free), $A_V$ and $R$ are free for
%%each supernova, with a uniform prior $-0.21\le A_V \le 1.8$, $2.1 \le R \le 6.9$.
%
%Results from evaluating this model with SNf data
%provide further evidence of the inconsistency between the ansatz and the models of the previous section.
%The dust-model analysis of this section sets the magnitude of an $A_V=0$ supernova, so now  magnitudes of the canonical
%supernova in \S\ref{model:sec} can also be compared (along with color) to the expectations of the dust model.  The magnitude difference, $\Delta c_X$,
%is the difference between the $c_X$ parameters of the two analyses.
%Then  $\Delta c_X / (\Delta c_B - \Delta c_V)$
%corresponds to  $A_X/E(B-V)$ of the canonical supernova relative
%to SALT2: these values are plotted in
%Figure~\ref{model1118:fig}.
%The negative values for $X=BVRI$ and the non-monotonic behavior is inconsistent with the expectations of dust.
%
%The analysis results for the dust parameters are shown in Figure~\ref{AVRV:fig}.  The left plot shows the histogram of the median $A_V$ determined for
%each supernova. The
%$A_V$ distribution  has a slow rise from zero; recall that the equivalent $\gamma^0_V k_0$
%from the linear model of \S\ref{model:sec} has the sharp rise expected from of a large fraction of supernovae
%experiencing no dust \citep{1998ApJ...502..177H}. The right plot shows the posterior of $R$, with 68\% credible interval
%$R=2.99^{0.18}_{-0.16}$.  We perform the same analysis using the updated template of \citet{2007ApJ...663.1187H} in place of SALT2.
%While the $A_V$ distributions using the different models appear similar, there is a significant shift in the $R$ distribution
%to $R=3.17^{0.20}_{-0.17}$.
%
%
%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%   \centering
%   \includegraphics[width=2.8in]{output18/AVs_mode_hist.pdf}
%   \includegraphics[width=2.8in]{output18/RVs_hist.pdf}
%    \caption{Left: Histogram of the median $A_V$ determined for
%each supernova.  The $\gamma^0_V k_0$ medians from our 2-parameter model of \S\ref{model:sec} is also shown.  The means of the measurement
%uncertainty over all supernovae are 0.13,   0.16,   0.11, and  0.05 mag respectively, roughly the size of the bin.
%Right: Posteriors for $R$.  Results for both the SALT2 supernova model and the updated \citet{2007ApJ...663.1187H} are shown.
%   \label{AVRV:fig}}
%\end{figure}
%
%The broadband nature of our supernova model does not allow a precise specification for the prediction of dust models,
%and our ansatz for incorporating dust is limited systematically in measuring 
%the total-to-selective extinction.  We emphasize also that $R^F$ determined in this section are based on  both absolute extinction and color,
%whereas the $\gamma$'s (and resulting $\kappa_1$) in \S\ref{model:sec} do not depend on absolute extinction, i.e. the extra model constraint  of the
%zero-extinction supernova.
%
%
%%
%%The $R$-free analysis is performed for the dust law of \citet{1989ApJ...345..245C}.  Figure~\ref{CCMF99:fig} shows the difference between per-supernova
%%$A_V$ and $R_V$ of  the  \citet{1989ApJ...345..245C} (superscripted with $C$) and \citetalias{1999PASP..111...63F} dust laws.
%%The weighted mean of the difference in $A_V$ is $0.06 \pm 0.01$ mag and that of $R_V$ is $-0.26 \pm 0.09$, both significantly
%%non-zero.  Insofar that the $A_V$ and $R_V$
%%parameters of the two models are designed to represent the same dust observables, we find that the systematic uncertainty in the dust model itself
%%is important.
%%
%%
%%\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
%%   \centering
%%   \includegraphics[width=5.2in]{output18/CCMf99.pdf}
%%    \caption{Difference between per-supernova
%%$A_V$ and $R_V$ of the  \citet{1989ApJ...345..245C} and \citetalias{1999PASP..111...63F} dust laws.
%%   \label{CCMF99:fig}}
%%\end{figure}
%
%
%\color{black}
\section{Discussion and Summary}
\label{discussion:sec}

@@

\color{blue}
An interesting direction for future work is to use narrower bands for generating synthetic photometry.  When the bandwidth were small enough
to resolve spectral features, the analysis would produce a spectroscopic model.   Higher resolution would allow us to forego 
the use of a fiducial template necessary to predict broadband fluxes generated by dust models, and also allow direct incorporation
of dust models into our framework.
\color{black}
